Figures

### 2020-02-26 manuscript/figures.Rmd
outline figures todo

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{colortbl}
---

\arrayrulecolor{white}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, dev = c("pdf"))
```

@@

![Diagram showing the assumption of most lake depth models that the nearshore slope is extends into the lake and that all lakes have a common relationship between nearshore and in-lake slope. ](../figures/slope_diagram.pdf){width=85%}

![Diagram showing our expectation that slope-based models of lake depth will under predict true depth in convex lakes (left) and over predict true depth in concave lakes (right)](../figures/lake_shape.pdf){width=85%}

```{r lgnemanual-vs-bathy-depth, fig.cap="Comparison between reported max depth and max depth calculated from bathymetry surfaces.", warning=FALSE, echo = FALSE, eval=TRUE}
# see 00_qa.Rmd
knitr::include_graphics("../figures/lgnemanual-vs-bathy-depth-1.pdf")
```

```{r maps_dot_bathy, fig.cap = "Map of lake maximum depth measurements calculated from lake bathymetry surfaces.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map_bathy-1.pdf")
```

```{r 01_geometry_grid, fig.cap = "Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) buffer slope versus inlake slope.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_geometry_grid-1.pdf")
```

>>>>

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{colortbl}
- \usepackage{float}
---

\arrayrulecolor{white}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, dev = c("pdf"))
knitr::opts_chunk$set(fig.pos = 'H')
```

@@

![Diagram showing the assumption of most lake depth models that the nearshore slope is extends into the lake and that all lakes have a common relationship between nearshore and in-lake slope. ](../figures/slope_diagram.pdf){width=75%}

```{r lake_shape, echo=FALSE, out.extra='', fig.align='center', fig.cap="Diagram showing our expectation that slope-based models of lake depth will under predict true depth in convex lakes (left) and over predict true depth in concave lakes (right)"}
knitr::include_graphics("../figures/lake_shape.pdf")
```

```{r maps_dot_bathy, fig.cap = "Map of study lakes showing A) lake maximum depth measurements, B) cross-section shape class, and C) reservoir classification.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/00_map_bathy-1.pdf")
```

```{r lgnemanual-vs-bathy-depth, fig.cap="Comparison between reported max depth and max depth calculated from bathymetry surfaces.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
# see 00_qa.Rmd
knitr::include_graphics("../figures/lgnemanual-vs-bathy-depth-1.pdf")
```

### predictor summary table

### variable importance for true slopes and distances (5)

### model metrics grid (table)

### 2 x 4 grid of residual box plots for shape and reservoir by true and proxy dist/slope (6)

### 4 x 2 grid of dotplots of depth, slope, area, dist by shape and reservoir class (7)

# Appendix

```{r 01_geometry_grid, fig.cap = "Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) buffer slope versus inlake slope.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/01_geometry_grid-1.pdf")
```
